\plaintitle

### 2016-09-21 drafts/labor/relationships.tex

\subsubsection{\implication}
\topic{What we've done in the field of crowd work might be able to tell us something about piecework
just as piecework has told us so much about crowd work.}
Crowd work research doesn't just benefit from
digital media allowing us to make
relationship networks like \citeauthor{crowdcollab} do;
we benefit from the firmer theoretical basis of Anthropology that
existed in a radically different form at the turn of the \nth{20} century,
when piecework began to emerge.
\citeauthor{malinowski2002argonauts,boas1940race,mead1973coming} and
other luminaries throughout the first half of the \nth{20} century
effectively defined Cultural Anthropology as we know it today;
\textit{participant--observation},
the \textit{etic} and the \textit{emic} understanding of culture, and
\textit{reflexivity}
didn't take even a resemblance of their contemporary forms until these works
\cite{malinowski2002argonauts,boas1940race,mead1973coming}.

\topic{The research on piecework still offers to guide us on perhaps the most rudimentary aspects of worker management}
\citeauthor{10.2307/2555446} drew a dichotomous line between
``defective (simple, observable) output measures'' and
``a manager's subjective judgment'',
but such a dichotomy need not necessarily represent our work management styles
\cite{10.2307/2555446}.
We can develop tools that better inform humans, rather than
(perhaps futilely) attempt to delegate all worker management to machines.
This is an area we should pursue, but haven't yet.
If the literature on piecework is to be believed,
more considerate \textit{human} management may resolve
many of the tensions we've discovered among among crowd workers.

>>>>

\subsubsection{\implication}

%	*workers make little money but love autonomy --- workers make little money
%	workers blamed for quality --- ???
%	both cases, sociality is hard
%	*collective action hard --- collective action succeeded
%	- algorithms, not managers

The decentralization and anonymization of crowd work will continue to make many of its social relationships a struggle.
While some workers get to know each other well on forums~\cite{martin2014being,crowdcollab}, many never engage in these social spaces.
Without intervention, worker relationships and collectivism are likely to be inhibited by this decentralized design.
One option is to build worker centralizing points into the platform, for example asking workers to vote on each others' reputation or allowing groups of workers to collectively reject a task from the platform~\cite{crowdguilds}.

\topic{The history of piecework further suggests that relationships between workers and employers might be improved if employers engaged in more human management styles.}
% \citeauthor{10.2307/2555446} drew a dichotomous line between
% ``defective (simple, observable) output measures'' and
% ``a manager's subjective judgment'',
% but such a dichotomy need not necessarily represent our work management styles
% \cite{10.2307/2555446}.
Instead of delegating as many management tasks as possible to an algorithm, it might be possible to build dashboards and other information tools that empower modern crowd work foremen~\cite{kulkarni2012mobileworks}.
If the literature on piecework is to be believed,
more considerate \textit{human} management may resolve
many of the tensions we've discovered among among crowd workers.

\topic{Reciprocally, crowd work may be able to inform piecework research.}
There exists far less literature about pieceworkers' relationships than there does today about crowd workers' relationships.
Crowd work research benefits from both the accessibility of digital platforms, as well as the firmer theoretical basis of Anthropology than
existed at the turn of the \nth{20} century, when piecework began to emerge.
\citeauthor{malinowski2002argonauts,boas1940race,mead1973coming} and
other luminaries throughout the first half of the \nth{20} century
effectively defined Cultural Anthropology as we know it today;
\textit{participant--observation},
the \textit{etic} and the \textit{emic} understanding of culture, and
\textit{reflexivity}
didn't take even a resemblance of their contemporary forms until these works
\cite{malinowski2002argonauts,boas1940race,mead1973coming}.
Modern crowd work may give us an opportunity to revisit open questions in piecework with a more refined lens.
